Catchy Title Goes Here

### 2018-06-20 Paper/paper.tex
updates to discussion text.

\begin{figure*}
\includegraphics[width=0.9\textwidth,angle=0]{figures/SimPlots-crop.pdf}
\caption{\label{fig:simplots} Results from study using simulated data. 
The top left plot shows the posterior distributions for each of four different datasets generated with four different vaccine effectiveness ($\gamma$). The injected values are shown as dashed lines, and the recovered distributions are labelled with the associated value of $\gamma$. The prior is shown as a solid yellow line. The top panel of this plot is generated using all three datasets, and the bottom panel uses only vaccination and serology data. We find that the recovered value of $\gamma$ is typically biased low, but that the ordering of datasets by $\gamma$ is recovered correctly. In the cases of high $\gamma$ and no serology data, the recovered posteriors are dominated by the prior.
The top right plot shows the injected (dashed) and recovered (solid) force of infection (top panel) and vaccination hazard (bottom panel) for the same four datasets. The Weibull is not a good fit to the injected foi, but the resulting fits to the observable data (bottom plot) are not overly biased. The fit to the vaccination hazard is similarly not perfect, and the overly-high peaks can explain the general biasing of $\gamma$ to low values. 
The bottom plot shows the injected (points) data and recovered (lines) curves for the highest (orange) and lowest (indigo) values of $\gamma$ for seroprevalence data (top), vaccination data (middle), and case data (bottom).}
\end{figure*}

@@

\section{Discussion \label{sec:Discussion}}
Discussion:

Application for estimating seroprevalence in settings where a sero-survey is not possible 
	? serosurvey may not be feasible to do frequently, but this allows us to use passively collected age-specific case incidence 
	? doing a very wide serosurvey may not be feasible, or practical, but case surveillance lets you see signal across a wide age range

What is the use of this?
	? estimating seroprevalence in the absence of surveys
	? effect size estimate for designing sero-surveys

Discuss the interpretation of the patterns seen in the DRC data 
	? which places have good vaccination, which have high transmission
	? As I recall, some provinces have very wide FOI hazards, indicating that some people are getting infected relatively late in life.  There are lots of possible reasons for this, so should give it some thought.  Could relatively low exposure, so some people are just not exposed until late in life.  Could also reflect inflow of internally displaced people (IDPs).  Speculation depends on the pattern.

Several things that we haven?t dealt with here, that we?ll need to at least acknowledge:
	- we haven?t dealt with the fact that incidence and vaccination are not stationary
	- we haven?t dealt with supplemental campaigns
	- these are all things that can be dealt with at least theoretically

Take-home message about merging serosurveillance and case-based surveillance

>>>>

\begin{figure*}
\includegraphics[width=0.9\textwidth,angle=0]{figures/SimPlots-crop.pdf}
\caption{\label{fig:simplots} Results from study using simulated data. 
The top left plot shows the posterior distributions for each of four different datasets generated with four different vaccine effectiveness ($\gamma$). The injected values are shown as dashed lines, and the recovered distributions are labelled with the associated value of $\gamma$. The prior is shown as a solid yellow line. The top panel of this plot is generated using all three datasets, and the bottom panel uses only vaccination and serology data. We find that the recovered value of $\gamma$ is typically biased low, but that the ordering of datasets by $\gamma$ is recovered correctly. In the cases of high $\gamma$ and no serology data, the recovered posteriors are dominated by the prior.
The top right plot shows the injected (dashed) and recovered (solid) force of infection (top panel) and vaccination hazard (bottom panel) for the same four datasets. The Weibull is not a good fit to the injected foi, but the resulting fits to the observable data (bottom plot) are not overly biased. The fit to the vaccination hazard is similarly not perfect, and the overly-high peaks can explain the general biasing of $\gamma$ to low values. 
The bottom plot shows the injected (points) data and recovered (lines) curves for the highest (orange) and lowest (indigo) values of $\gamma$ for seroprevalence data (top), vaccination data (middle), and case data (bottom). Solid points indicate observations between 5-59 months, the age range observed in the 2014 DHS survey, and the open points give observations greater than 59 months. }
\end{figure*}

@@

\section{Discussion \label{sec:Discussion}}

The age-specific profile of immunity to measles infection can be a powerful tool for the assessment of vaccination programs and the planning for vaccine-based interventions [REF - Winter; Cutts and Hanson]. Comprehensive serological surveys can be prohibitively expensive and are thus only conducted infrequently.  Age-specific measles case incidence, by contrast, is routinely collected in most national health systems and has been previously used to infer age-specific infection risk via the catalytic model [REF - Griffiths; Grenfell and Anderson; Whittaker and Farrington; Ferrari 2010]. Here we present a novel extension of the catalytic model that uses age-specific vaccination coverage surveys to account for the competing age-specific rates of immunization via vaccination and natural infection.  We show, using a simulation experiment, that this model can be used to estimate age-specific seroprevalence using age-specific case incidence and vaccination coverage data. A necessary component of this model is the vaccine effectiveness, which gives the proportion of individuals who report vaccination on a survey that are effectively immunized by vaccination.  We show that, while this vaccine effectiveness is difficult to estimate in absolute value, our model-based estimator is positively correalted with the true value used in simulation; thus this estimate may be useful as a relative measure of vaccine effectiveness.  We further show that the inclusion of limited serological survey data, here a survey of children between 6-59 months of age, results in improvements of all model parameters, including vaccine effectiveness.

We applied our novel catalytic model to age-specific measles case, vaccination survey, and serological survey data from the DRC. The coincidence of a vaccination and serological survey in DRC during the 2014 DHS presents an opportunity to test the model fit using only case incidence and vaccination survey data to the directly measured measles seroprevalence. We show that, for most provinces, the age-specific seroprevalence estimated using only age-specific measles case and vaccination survey data is a reasonable approximation of the observed seroprevalence (FIG REF 2). We note, however, that the estimated seroprevalence was occassionaly biased in a direction that would over-estimate population immunity and under-estimate measles outbreak risk.

The 2014 DHS in DRC included a sero survey that was limited to children between the ages of 6-59 months.

That survey provides only a limited perspective on the immunity in older age classes.  The case data, however DO provide this information.  This raises the question of what is the marginal benefit of conducting a sero survey.

very little marginal benefit in terms of assessing relative risk -- the age-specfic case data and vaccination coverage data do a good job of estimating the rank order of risk.

However, as illustrated in the simulation study, the sero survey allows more confident estimates of the rank order of vaccine effectiveness.

Limitations -- the model requires some significant assumptions that are almost certainly violated.

Applications -- design of sero surveys.

Periodic assessment of sero-prevalence.

%Discussion:

%Application for estimating seroprevalence in settings where a sero-survey is not possible 
%	? serosurvey may not be feasible to do frequently, but this allows us to use passively collected age-specific case incidence 
%	? doing a very wide serosurvey may not be feasible, or practical, but case surveillance lets you see signal across a wide age range

%What is the use of this?
%	? estimating seroprevalence in the absence of surveys
%	? effect size estimate for designing sero-surveys

%Discuss the interpretation of the patterns seen in the DRC data 
%	? which places have good vaccination, which have high transmission
%	? As I recall, some provinces have very wide FOI hazards, indicating that some people are getting infected relatively late in life.  There are lots of possible reasons for this, so should give it some thought.  Could relatively low exposure, so some people are just not exposed until late in life.  Could also reflect inflow of internally displaced people (IDPs).  Speculation depends on the pattern.

%Several things that we haven?t dealt with here, that we?ll need to at least acknowledge:
%	- we haven?t dealt with the fact that incidence and vaccination are not stationary
%	- we haven?t dealt with supplemental campaigns
%	- these are all things that can be dealt with at least theoretically

%Take-home message about merging serosurveillance and case-based surveillance
